\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

\newcommand{\certificationHeading}[3]{\textbf{#1}\hspace*{\fill}{#2}\\}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Avnish Pal}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{www.bovem.in}
% vs how you want it to show up. If it's the same you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://www.bovem.in}
\newcommand{\yourEmail}{avnishnish07@gmail.com}
\newcommand{\yourPhone}{+918588064883}
\newcommand{\githubUserName}{bovem}
\newcommand{\linkedInUserName}{avnish-pal}

% An alternate profile section 
% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
%     \\
% \end{tabular*}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
     \small \href{\yourWebsiteLink}{\underline{\yourWebsite}} $|$
     \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone \ $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
    
\end{center}


%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{Red Hat}{Associate Software Quality Engineer }{Pune, India}{Jan 2022 - Present}
\begin{bullets}
        \item \textbf{API and Integration Testing: } Implemented unit and integration tests for all the API services associated with OpenShift Operator Certification.
        \item \textbf{Chat Bot for Status Updates: } 
        Created a Python based chat bot for hourly automation status updates.
        \item \textbf{File Server: } Added updation and deletion operations to a Django based file server.
\end{bullets}
\sectionsep

\resumeHeading{Red Hat}{Intern}{Pune, India}{Jun 2021 - Dec 2021}
\begin{bullets}
        \item \textbf{RHEL Certification: } Implemented automation for testing RHEL beta OS builds on GCP and Azure.
        \item \textbf{Montoring Dashboard: } 
        Created a Django dashboard for monitoring of OS image builds
\end{bullets}
\sectionsep

\resumeHeading{Taiyo AI}{Software Engineer}{Remote}{Sep 2019 - Jun 2021}
\begin{bullets}
        \item \textbf{Analytics Dashboard: } Created Grafana and Django based procurement analytics dashboards for clients such as Tata
Steel, Bouygues, and Bloomenergy.
        \item \textbf{Trading Agent: } 
        Contributed on a trader agent that benchmark-ed at 22\% annual returns, consistently beating S\&P
500.
        \item \textbf{Asset Recommentation Tool: } Created an asset recommendation tool for investors that shortlists the top 10 assets from
S\&P 500 index for investment.
\end{bullets}
\sectionsep

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}

\projectHeading{Stock Portfolio Optimization strategies}{https://github.com/bovem/portfolio-sim}{Python, Pyportfolioopt, Django, Dash, ML}
Created modules for fetching, cleaning and processing intraday
OHLC data from NSE. Backtested portfolio optimization algorithms in a stock market simulation environment.\\
\sectionsep
  
\projectHeading{Data Pipeline GUI}{https://github.com/bovem/DataWiz}{Python, Django, Dash, Data Analysis}
End-to-End data science pipeline application. Supports data import, processing, cleaning, visualization,
machine learning algorithms and export.\\
\sectionsep

\projectHeading{Flutter Mobile Application}{https://github.com/bovem/Courser}{Dart, Flutter, Firebase, Android Development}
Search engine for online learning resources. Supports user contributions, reviews, and upvotes.
\sectionsep

\projectHeading{Stock Screener}{https://github.com/bovem/stock-tracker}{Python, Dash, Pandas, Data Analysis}
An interactive data visualization application developed in Python, with the help of Dash , yfinance and Pandas.\\
\sectionsep

\projectHeading{Personal Portfolio and Blog}{https://github.com/bovem/old.bovem.github.io}{Jekyll, Bootstrap, Blog}
 Jekyll based website hosted on Netlify.\\
\sectionsep

% Example using bullets and dates 
% \projectHeadingWithDate{Hogwart\textquotesingle{}s Library Management System}{https://github.com/Aarif123456/hogwartslibrary}{PHP, JavaScript, HTML, CSS, MySQL}{Aug 2019}
% \begin{bullets}
    % \item A full-stack library management system, where users can manage books and holds on their accounts. Users can search the library\textquotesingle{}s catalogue, which has every book mentioned in the Harry Potter series. The system distinguishes between 4 users. For examples, librarians who can also check or return books on behalf of users.\\
% \end{bullets}
% \sectionsep
  
%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{Bachelor of Technology in IT}{Guru Gobind Singh Indraprastha University}{Delhi, India}{Jun 2021}

\courseWork{Operating Systems, Database Management Systems, System Design, Data Structures and Algorithms}
\sectionsep

%--------------------------------------------------------------
%     Certifications
%--------------------------------------------------------------
\section{Certifications}
% Put school first and degree second if your school is reputable
\certificationHeading{Red Hat Certified Specialist in Containers and Kubernetes}{Podman, Kubernetes, OpenShift}\\
\certificationHeading{Red Hat Certified System Administrator (RHCSA)}{Bash, Linux, RHEL8}\\
\sectionsep

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
    \singleItem{Programming Languages:}{Python, C++, JavaScript, SQL, Bash, Java}
    \\
    \singleItem{Frameworks:}{Tekton, Scikit, TensorFlow, Django, Flask}
    \\
    \singleItem{Technology:}{Kubernetes, Docker, GIT, OpenShift, PostgreSQL, MySQL, SQLite}
    \\
    \singleItem{Platforms:}{Linux, AWS, GCP, IBM Cloud}
\end{skillList}

% A more concise alternate 
% \begin{skillList}
%     \doubleItem{Languages:}{Java, C++, Python, C\#, PHP, Prolog, Bash, C, Racket}%
%     {Databases:}{SQL, MongoDB, Neo4j, DynamoDB}
%     \\
%     \doubleItem{Web Development:}{JavaScript, TypeScript, React, HTML/CSS}
%     {Technology:}{Git, AWS, GCP, Azure, Docker, \LaTeX}%
% \end{skillList}
\end{document}